Contextual Identity: Towards Usable Privacy

### 2013-02-28 paper.tex
More rewrites for intro

\author{Monica Chew,Sid Stamm\\
\tt{\{mmc,sid\}@mozilla.com}}
%\institute{Mozilla}
\maketitle

\begin{abstract}
We examine \textit{contextual identity}, a notion that individuals reveal
different aspects of themselves depending on context. At any given time, they
may act as a friend, relative, spouse, co-worker, aquaintance, or stranger. We
analyze contextual identity from the perspective of user choice and control,
survey contextual identity violations, suggest possible mitigations, and
propose new resesarch directions to empower users to have better control over their contextual identities.
\end{abstract}
\section{Introduction}
\begin{quote}I am large, I contain multitudes. --- Walt Whitman,
\begin{em}Song of Myself\end{em} \end{quote}

@@

\begin{verbatim}
NEED NEW EXAMPLE
gay teen joins facebook group
megan meier
amanda todd
tyler clementi
http://www.sync-blog.com/sync/2012/10/gay-students-outed-by-facebook-privacy-loophole.html
http://books.google.ca/books?id=RRUkLhyGZVgC&pg=PA199&lpg=PA199&dq=%22The+days+of+you+having+a+different+image+for+your+work+friends+or+co-workers+and+for+the+other+people+you+know+are+probably+coming+to+an+end+pretty+quickly,%22&source=bl&ots=LRUZf_pd9m&sig=oHHi0qhlHh9prk94gCQFXItjGIg&hl=en&sa=X&ei=ma19UIOhAdOEqQHE2oCADA&ved=0CD8Q6AEwBA#v=onepage&q=%22The%20days%20of%20you%20having%20a%20different%20image%20for%20your%20work%20friends%20or%20co-workers%20and%20for%20the%20other%20people%20you%20know%20are%20probably%20coming%20to%20an%20end%20pretty%20quickly%2C%22&f=false
\end{verbatim}

In offline environments, managing contextual identities is more intuitive than
in online environments. There are cues to help you determine where you are,
who your intended audience is, how many people will overhear you, and how
likely your information is to be re-broadcast in a different context. It is
also true that in offline environments, humans don't have perfect memories and
will eventually forget.  However, with the advent of increasingly vast
searching, indexing, and archiving capabilities, one cannot rely on forgetting
in online environments~\cite{delete}. Managing contextual identities
online has become increasingly difficult and fraught with mistakes.

@@

Although network inference and merging attacks are very powerful, at the
current time they require a level of expertise and resources not available to
most people. A brief survey of social networking advice reveals that the major
causes of concern come not from a dedicated social graph expert, but people
close to the user: friends, family, and co-workers~\cite{fbtips2,fbtips1}.
Surveys conducted by Wang et al.~show that typical regrets from posting on
Facebook stem almost exclusively from fear of negative interactions with people
that the user knows~\cite{wang}. The consequences of these negative
interactions can lead to loss of employment or breaking personal relationships.
Most previous privacy research has focused on distant adversaries, where the
bad actor is a behavioral tracking service, state agent or unknown
eavesdropper; in contrast, we assert that users care more about their
interactions with others close to them.

@@

\subsection{User interface errors}
Even in the absence of changes made by service providers to re-contextualize
personal information, it is all too easy for users to broadcast information to
an unintended audience. This phenomenon is so common on Twitter that it has its
own name, ``DM fail'', or Direct Message fail: when the user posts a public
message instead of a private, direct message. Representative Anthony Weiner was
a victim of this mistake when he inadvertently sent compromising pictures of
himself publicly~\cite{weiner}. Considering that this mistake requires
mistyping a single character (\texttt{@} instead of \texttt{d}), it's no
surprise that DM failures are exceedingly common.

@@

\subsection{Third party tracking}
\label{sec:tracking}
Even if a user does not participate in social networks, they are still subject
to tracking by virtue of browsing the web. Third-party cookies, flash cookies,
web bugs, device fingerprinting, geolocation, history sniffing and more are
techniques that a dedicated third party could use to collect browsing history
and link contextual identities through correlation of tasks.

\section{Possible mitigations}

@@

\subsection{Automatic mitigations for information leakage}
Given a set of relationships and tasks, one can categorize a user's
contextual identities and prevent information leakage between them.  For
example, preventing third-party cookies from being read and set across task
boundaries means that targeted ads for dating would not follow the user when
visiting a technology news site. Knowing the user's current contextual identity
also allows the browser to suppress URL bar suggestions that aren't relevant to
that identity, protecting the user from both shoulder-surfing and distraction.

@@

Profiles can be generated by user-supplied application-level data, but also
implicitly through browsing via techniques in Section~\ref{sec:tracking}.
Collusion is a tool for visualizing cookies~\cite{collusion}, in particular
third-party cookies set by tracking sites which are typically ad networks.
Once the user knows which sites are tracking them, they can choose to block
cookies from those sites.

@@

\section{How do users think about identity?}
\subsection{Blushproof}
\subsection{Cookie statistics}

\section{Open problems}
We are largely ignorant of the ways in which users think about contextual
identity. Building usable software to manage contextual identity demands
further research.

The mitigations proposed in this work become more complex in the face of shared
devices and overlapping identities. There are good reasons to want to intermix
work and personal identities (increased exposure, serendipitous connections)
and so many people use the same account for both personal and work reasons.

Mobile growth is driving most internet growth, and much of that growth comes
developing countries. The literature on how device sharing works in those
markets is completely lacking. Managing contextual identities on shared devices
promises to be a difficult problem.

\section{Discussion}
People have multiple contextual identities. Sharing personal information in
appropriate contexts fosters positive human interaction.  We hope that
contextual identity will serve as a useful notion for developers to understand
their users' privacy needs, and to develop tools that allow users to act in
their contextual identities in a spontaneous, relaxed, and interesting way.

\begin{comment}
papers:
expectation of privacy\cite{viegas}
http://jcmc.indiana.edu/vol10/issue3/viegas.html

danah boyd
making sense of privacy and publicity: whose voice counts? does your child's
teacher have a right to be public in her other roles online? does she have a
right to be secular? religious? friend? lover? if you work for company X and
you disagree with their policies, are you allowed to be public about
that:?\cite{boyd2}

close to you “stranger on a train” “stranger on a plane”
first party regrets, third party regrets
impossible to judge how big friends of friends

\end{comment}

>>>>

\author{\IEEEauthorblockN{Monica Chew, Sid Stamm}
\IEEEauthorblockA{Mozilla\\
\tt{\{mmc, sid\}@mozilla.com}}
}
\maketitle

\begin{abstract}
We examine \textit{contextual identity}, a notion that individuals reveal
different aspects of themselves depending on context. At any given time, they
may act as a friend, relative, spouse, co-worker, aquaintance, or stranger. We
analyze contextual identity from the perspective of user choice and control,
survey contextual identity violations, and propose new resesarch directions to
empower users to have better control over their contextual identities.
\end{abstract}

\section{Introduction}
\begin{quote}I am large, I contain multitudes. --- Walt Whitman,
\begin{em}Song of Myself\end{em} \end{quote}

@@

We consider it a contextual identity violation when
multiple contextual identities are linked without the user's permission, or the
user cannot control which contextual identity is presented to a given audience.

Lesbian, gay, bisexual, and transgendered youth are a prime example of this.
Access to support is crucial for LGTB-identified youth who are at higher risk
for bullying and suicide than non-LGTB youth, and much of that support is only
accessible through the Internet in socially conservative areas~\cite{hrc}. In
2011 Bobbi Duncan and Taylor McCormick, two students at the University of Texas
at Austin, were inadvertantly outed when their choir director added them to a
Facebook group for Queer Chorus~\cite{fowler}. Even though both students had
blocked their parents from seeing any personal posts revealing their sexuality,
because Queer Chorus is a public group Facebook published notifications to
Duncan's and McCormick's friends, including their parents. Duncan later
attempted suicide~\cite{duncan}.

\begin{comment}
zuckerberg on "having multiple identities is dishonest"
http://books.google.ca/books?id=RRUkLhyGZVgC&pg=PA199&lpg=PA199&dq=%22The+days+of+you+having+a+different+image+for+your+work+friends+or+co-workers+and+for+the+other+people+you+know+are+probably+coming+to+an+end+pretty+quickly,%22&source=bl&ots=LRUZf_pd9m&sig=oHHi0qhlHh9prk94gCQFXItjGIg&hl=en&sa=X&ei=ma19UIOhAdOEqQHE2oCADA&ved=0CD8Q6AEwBA#v=onepage&q=%22The%20days%20of%20you%20having%20a%20different%20image%20for%20your%20work%20friends%20or%20co-workers%20and%20for%20the%20other%20people%20you%20know%20are%20probably%20coming%20to%20an%20end%20pretty%20quickly%2C%22&f=false
\end{comment}

In offline environments, managing contextual identities is more intuitive than
in online environments. There are cues to help you determine where you are,
who your intended audience is, how many people will overhear you, and how
likely your information is to be re-broadcast in a different context. It is
also true that in offline environments, humans don't have perfect memories and
will eventually forget.  However, with the advent of increasingly vast
searching, indexing, and archiving capabilities, one cannot rely on forgetting
in online environments~\cite{delete}. Managing contextual identities
online has become increasingly difficult and fraught with mistakes; we must
provide users with better tools to control their contextual identities.

@@

Evidence suggests that users' major privacy concerns come from people the user
knows: friends, family, and co-workers~\cite{fbtips2,fbtips1}.  Surveys
conducted by Wang et al.~suggest that typical regrets from posting on Facebook
stem almost exclusively from fear of negative interactions with people that the
user knows~\cite{wang}. The consequences of these negative interactions can
lead to loss of employment or breaking personal relationships.  Most previous
privacy research has focused on distant adversaries, where the bad actor is a
behavioral tracking service, state agent or unknown eavesdropper; in contrast,
we assert that users care more about their interactions with others close to
them.

@@

\subsection{User interface errors}
It is all too easy for users to broadcast information to
an unintended audience. This phenomenon is so common on Twitter that it has its
own name, ``DM fail'', or Direct Message fail: when the user posts a public
message instead of a private, direct message. Representative Anthony Weiner was
a victim of this mistake when he inadvertently sent compromising pictures of
himself publicly~\cite{weiner}. Considering that this mistake requires
mistyping a single character (\texttt{@} instead of \texttt{d}), it's no
surprise that DM failures are exceedingly common.

@@

\section{Research directions}
We propose new research directions based on the following questions.
\begin{itemize}
\item How do users think about identity?
\item What are users already doing to preserve contextual identities?
\item What tasks or topics do users find embarrassing?
\end{itemize}

plethora of cross posting software, too much damn syndication indicates that
many users are on multiple platforms.

@@

\subsection{Automatic mitigations for information leakage}
One can categorize a user's contextual identities and prevent information
leakage between them.  For example, preventing third-party cookies from being
read and set across task boundaries means that targeted ads for dating would
not follow the user when visiting a technology news site. Knowing the user's
current contextual identity also allows the browser to suppress URL bar
suggestions that aren't relevant to that identity, protecting the user from
both shoulder-surfing and distraction.

@@

Profiles can be generated by user-supplied application-level data, but also
implicitly through browsing via tracking techniques.
Collusion is a tool for visualizing cookies~\cite{collusion}, in particular
third-party cookies set by tracking sites which are typically ad networks.
Once the user knows which sites are tracking them, they can choose to block
cookies from those sites.

@@

\section{Summary}
People have multiple contextual identities. Sharing personal information in
appropriate contexts fosters positive human interaction.  We hope that
contextual identity will serve as a useful notion for developers to understand
their users' privacy needs, and to develop tools that allow users to act in
their contextual identities in a spontaneous, relaxed, and interesting way.
